Best Practices for Alchemical Free Energy Calculations: v\versionnumber

### 2020-01-09 paper/manuscript.tex
Add references to cycle closure and a paragraph on reversible binding simulations as a validation.

\subsubsection{Are my simulations any good?}
One way of assessing reliability of the calculations is checking the phase space overlap between neighboring $\lambda$-windows~\cite{wu2005phasespace,wu2005phasespacea}. For this purpose, a so-called overlap matrix can be used. This is a $K\times K$ matrix, where $K$ is the number of simulated states, i.e. $\lambda$s. Sufficient overlap is important for reweighting estimators such as BAR or MBAR, but cannot help assess reliability of estimates, when using TI. 
These matrices are graphical representations of the phase space overlap, i.e. the average probability that a sample generated at state $j$ can be observed at state $i$. As this probability is computed considering the samples from all states (and not just the adjacent states), the values in each row and column add up to 1. In this analysis, the goal is to ensure every state has overlap with its neighbors in both directions -- so that off-diagonal elements are significantly larger than zero. Usually this means the matrix should be at least tridiagonal.

@@

\paragraph{Cycle closure error}
Relative free energy calculations, which compute the change in free energy on making a change to a molecule (e.g. adding a functional group to a ligand) may provide an additional opportunity for error/consistency checking. Particularly, such calculations are often done to span a graph or tree of free energy calculations~\cite{LOMAP paper from Mobley group; Schrodinger 2015 JACS paper} and in some cases the free energy change to go between molecules A and B can be obtained via multiple transformation pathways. This allows a type of consistency checking where we assess how much the free energy change for that transformation in practice differs from equivalence. Significant deviations from this typically indicate insufficient configurational sampling along the lambda schedule of one or more of the transformations involved.

@@

A scheme to reduce cycle closure errors is used in FEP+ whereby calculated free energy changes along the nodes of the network are re-sampled assuming estimates of the calculated free energy change along a node may be obtained from a Gaussian distribution centered on the estimated free energy change and with a standard deviation equal to the estimated standard deviation of the free energy change. The procedure then uses a Maximum likelihood method to find new sets of free energy changes that minimize cycle closure errors~\cite{REF}. An alternative approach computes the free energy change between a target and reference compound as a weighted average over all unique paths in the network, with the weights derived from the propagated uncertainties of each node (REF).

@@

\section*{Author Contributions}
%%%%%%%%%%%%%%%%
% This section mustt describe the actual contributions of
% author. Since this is an electronic-only journal, there is
% no length limit when you describe the authors' contributions,
% so we recommend describing what they actually did rather than
% simply categorizing them in a small number of
% predefined roles as might be done in other journals.
%
% See the policies ``Policies on Authorship'' section of https://livecoms.github.io
% for more information on deciding on authorship and author order.
%%%%%%%%%%%%%%%%
\todo[inline, color={green!20}]{ASJSM: @everyone, can you check your contribution is acknowledge and if not add the appropriate information. }
(Explain the contributions of the different authors here)
ASJSM: Coordinated the document, contributed to most sections, and co-designed figures ~\ref{} and created figures \ref{fig:fig_what_is_lambda},~\ref{fig:fig1_what_is_alchemy},~\ref{fig:overlap} and replotted~\ref{fig:automatic-equilibration-detection} and improved ~\ref{fig:fig_types_of_networks}.
JS: created figures \ref{fig:fig_what_is_alchemy},~\ref{fig:fig_binding_thermodynamic_cycle},~\ref{fig:fig_topology},~\ref{fig:fig_mcss},~\ref{fig:fig_types_of_networks},~\ref{fig:fig_absolute_thermodynamic_cycle},~\ref{fig:scatterplot_analysis}, the data representation section, the checklist and contributed to general formatting discussions and editing.
MK: Contributed to the Data Analysis section, provided the data for figure~\ref{fig:overlap} and helped edit the paper.
DLM: Contributed to the outline, drafted some of the sections, gave ideas on figures, and helped edit the paper.
GT: Contributed to introduction and drug discovery sections, and helped edit the paper.
AR: Created figure~\ref{fig:freeenergytrajectories}, contributed to section \ref{sec:step2}, and helped edit the paper.
MRS: Helped create figure~\ref{fig:fig_what_is_lambda}, wrote sections describing choices for alchemical pathways and analysis for free energy calculations.
LN: \todo[inline, color={red!20}]{@Levi insert info here}
BA: \todo[inline, color={red!20}]{@Bryce insert info here}
JM: \todo[inline, color={red!20}]{@Julien insert info here}
JDC: \todo[inline, color={red!20}]{@JDC insert info here}
HX: Contributed section~\ref{subsec:accuracy} and to section~\ref{sec:relative-fe-protocol}.

>>>>

\subsubsection{Are my simulations any good?}
\label{sec:are-they-good}
One way of assessing reliability of the calculations is checking the phase space overlap between neighboring $\lambda$-windows~\cite{wu2005phasespace,wu2005phasespacea}. For this purpose, a so-called overlap matrix can be used. This is a $K\times K$ matrix, where $K$ is the number of simulated states, i.e. $\lambda$s. Sufficient overlap is important for reweighting estimators such as BAR or MBAR, but cannot help assess reliability of estimates, when using TI. 
These matrices are graphical representations of the phase space overlap, i.e. the average probability that a sample generated at state $j$ can be observed at state $i$. As this probability is computed considering the samples from all states (and not just the adjacent states), the values in each row and column add up to 1. In this analysis, the goal is to ensure every state has overlap with its neighbors in both directions -- so that off-diagonal elements are significantly larger than zero. Usually this means the matrix should be at least tridiagonal.

@@

\paragraph{Cycle closure error}
Relative free energy calculations, which compute the change in free energy on making a change to a molecule (e.g. adding a functional group to a ligand) may provide an additional opportunity for error/consistency checking. Particularly, such calculations are often done to span a graph or tree of free energy calculations~\cite{xu2019diffnet,wang2013modeling,liu2013lead} and in some cases the free energy change to go between molecules A and B can be obtained via multiple transformation pathways. This allows a type of consistency checking where we assess how much the free energy change for that transformation in practice differs from equivalence. Significant deviations from this typically indicate insufficient configurational sampling along the lambda schedule of one or more of the transformations involved.

@@

A scheme to reduce cycle closure errors is used in FEP+ whereby calculated free energy changes along the nodes of the network are re-sampled assuming estimates of the calculated free energy change along a node may be obtained from a Gaussian distribution centered on the estimated free energy change and with a standard deviation equal to the estimated standard deviation of the free energy change. The procedure then uses a Maximum likelihood method to find new sets of free energy changes that minimize cycle closure errors~\cite{wang2013modeling}. An alternative approach computes the free energy change between a target and reference compound as a weighted average over all unique paths in the network, with the weights derived from the propagated uncertainties of each node (REF).

\paragraph{Reversible binding simulations}
An even more stringent test of the correctness of binding free energy calculations is to compare the results to the equilibrium binding constants derived from long timescale reversible binding simulations~\cite{pan2017quantitative}.  For small ligands with millimolar affinities, repeated binding to and unbinding from the protein can occur for a large number of times in a sufficiently long unbiased MD simulation (10-100$\mu$s), and the equilibrium binding constants can be straightforwardly computed from the ratio of bound to unbound fractions of the simulation time.  The agreement between the binding free energy calculations and the reversible binding simulations--given the same system preparation and the same force field parameters--will strongly support the correctness of both calculations, as the same results are arrived at by two independent methods, and any discrepancy will suggest some systematic error in one, or both, of the two methods.  This test should be applied to all free energy calculation codes in the future.

@@

\section*{Author Contributions}
%%%%%%%%%%%%%%%%
% This section mustt describe the actual contributions of
% author. Since this is an electronic-only journal, there is
% no length limit when you describe the authors' contributions,
% so we recommend describing what they actually did rather than
% simply categorizing them in a small number of
% predefined roles as might be done in other journals.
%
% See the policies ``Policies on Authorship'' section of https://livecoms.github.io
% for more information on deciding on authorship and author order.
%%%%%%%%%%%%%%%%
\todo[inline, color={green!20}]{ASJSM: @everyone, can you check your contribution is acknowledge and if not add the appropriate information. }
(Explain the contributions of the different authors here)
ASJSM: Coordinated the document, contributed to most sections, and co-designed figures ~\ref{} and created figures \ref{fig:fig_what_is_lambda},~\ref{fig:fig1_what_is_alchemy},~\ref{fig:overlap} and replotted~\ref{fig:automatic-equilibration-detection} and improved ~\ref{fig:fig_types_of_networks}.
JS: created figures \ref{fig:fig_what_is_alchemy},~\ref{fig:fig_binding_thermodynamic_cycle},~\ref{fig:fig_topology},~\ref{fig:fig_mcss},~\ref{fig:fig_types_of_networks},~\ref{fig:fig_absolute_thermodynamic_cycle},~\ref{fig:scatterplot_analysis}, the data representation section, the checklist and contributed to general formatting discussions and editing.
MK: Contributed to the Data Analysis section, provided the data for figure~\ref{fig:overlap} and helped edit the paper.
DLM: Contributed to the outline, drafted some of the sections, gave ideas on figures, and helped edit the paper.
GT: Contributed to introduction and drug discovery sections, and helped edit the paper.
AR: Created figure~\ref{fig:freeenergytrajectories}, contributed to section \ref{sec:step2}, and helped edit the paper.
MRS: Helped create figure~\ref{fig:fig_what_is_lambda}, wrote sections describing choices for alchemical pathways and analysis for free energy calculations.
LN: \todo[inline, color={red!20}]{@Levi insert info here}
BA: \todo[inline, color={red!20}]{@Bryce insert info here}
JM: \todo[inline, color={red!20}]{@Julien insert info here}
JDC: \todo[inline, color={red!20}]{@JDC insert info here}
HX: Contributed section~\ref{subsec:accuracy}, to section~\ref{sec:relative-fe-protocol}, and to section~\ref{sec:are-they-good}.
